\chapter{Make A Directory (mkdir)}

\section{Do This}

\begin{code}{Linux/Mac OSX Exercise 4}
<< d['code/ex4.sh-session|pyg|l'] >>
\end{code}

\begin{code}{Windows Exercise 4}
<< d['code/ex4-win.sh-session|pyg|l'] >>
\end{code}

\section{You Learned This}

Now we get into typing more than one command.  These are all the different ways
you can run mkdir.  What's mkdir do?  It make directories.  Why are you asking
that?  You should be doing your index cards and getting your commands memorized.
If you don't know that "mkdir makes directories" then keep working the index
cards.

What does it mean to make a directory?  You might call directories "folders."  They're
the same thing.  All you did above is create directories inside directories
inside of more directories.  This is called a "path" and it's a way of saying
"first temp, then stuff, then things and that's where I want it."  It's a
set of directions to the computer of where you want to put something in the tree
of folders (directories) that make up your computer's hard disk.


\begin{aside}{Windows, Slashes And Backslashes}
In this book I'm using the \verb|/| (slash) character for all paths since they work
the same on all computers now.  However, Windows users will need to know that you can
also use the \verb|\| (backslash) characters and other Windows users will typically
expect those at times.
\end{aside}

\section{Do More}

\begin{enumerate}
\item The concept of a "path" might confuse you at this point.  Don't worry. We'll 
    do a lot more with them and then you'll get it.
\item Make 20 other directories inside the temp directory in various levels.  Go look at them
    with a graphical file browser.
\item Make a directory with a space in the name by putting quotes around it: \verb|mkdir "I Have Fun"|
\item If the \file{temp} directory already exists then you'll get an error.  Use \program{cd} to change to a work directory that you can control and try it there.  On windows \file{Desktop} is a good place.
\end{enumerate}

